Openness and computational reproducibility in plant pathology: where do we stand and a way forward

### 2022-08-25 analysis/paper/paper.Rmd
Define "code" and "data" in "code/data availability"
State that "code" includes ANY materials used in the analysis pipeline or model code, etc.

>>>>

For the purposes of this research paper, the word "code" in "code availability" was defined as including any materials that were used in the data import, cleaning, analysis, genome assembly or manuscript preparation or in the case of modelling papers, the model's software code itself.
The word "data" in "data availability" was defined as including any data created or collected and presented in the research manuscript.
